Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-07 src/article.tex
Revise discussion

Scaffolder is software aimed at bioinformaticians and biologists familiar with
the command line who wish to build a genome sequence scaffold. The file format
maintains the scaffold in a concise and readable way allowing third parties to
see how the genome sequence was assembled. This file format allows a broad
overview of of which sequences were included and how they are ordered,
something not possible from a megabase-length strings of nucleotide characters.
Scaffolder furthers the case for reproducibility in genome projects by allowing
the scaffold super-sequence to be reliably reproduced from the same scaffold
file. The YAML syntax for writing the scaffold file is also standardised and
simple to manipulate programmatically. This thereby means the scaffolding
process follows the Unix tenet of: ``If your data structures are good enough,
the algorithm to manipulate them should be trivial.''.

>>>>

Scaffolder is software aimed at bioinformaticians and biologists familiar with
the command line who wish to build a genome sequence scaffold from a set of
assembled contigs. The Scaffolder file format maintains the genome scaffold as
a concise and readable text representation that allows third parties to see how
the genome sequence was scaffolded. This file format also allows a broad
overview of which sequences were included and how they are ordered in the
genome scaffold, something not possible to deduce from a megabase-length
strings of nucleotide characters. Scaffolder furthers increases the ease of
reproducibility in genome projects by allowing the scaffold super-sequence to
be reliably reproduced from the same scaffold file. The YAML syntax for writing
the scaffold file is also standardised and simple to manipulate
programmatically. This thereby means the scaffolding process follows the Unix
tenet of: ``If your data structures are good enough, the algorithm to
manipulate them should be trivial.''.
